Interval Probability for Fuzzy Quantum Theories

### 2016-07-01 prob.tex
prob.tex Starting adding proof in appendix

\begin{definition}[Ideal Measurement; Complement;
Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e.,
$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal to $P$,
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\end{itemize}
\qed\end{definition}

@@

\end{document}

>>>>

\begin{definition}[Ideal Measurement; Complement;
Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e.,
$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal to $P$,
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\item For projection operators $P_{1}$ and $P_{2}$, we define $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$
if $P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}$ is a projection operator;
and $P_{1}\tensor*[_{\mathscr{O}}]{>}{}P_{2}$ if $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$
and $P_{1}\ne P_{2}$. Also, let $S_{i}$ be the linear subspace $P_{i}$
project onto, then $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$ if
and only if $S_{1}\supseteq S_{2}$.\yutsung{Need to verify!}
\end{itemize}
\qed\end{definition}

@@

\appendix

\section{Proof of Quantum Interval-valued Probability Measures}

Before we prove our results, we need the following lemmas.

\begin{lemma}Given a Hilbert space~$\Hilb$ with the set of quantum
events~$\events$, a collection of intervals~$\mathscr{I}$, and
a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
\qed\end{lemma}
\end{document}
